---
title: "Final Project"
author: "Jonathan Lynch"
subtitle: This is a test.
---

# Introduction
Something something Hazardous Materials something something.  

> I know words.  I have the best words.  ~ Donald Trump

# Materials and methods

Narrative and most code will go here.  Describe what you are doing and show how to do it (with code).

Plan for this project:

1. Create a map of Erie County
2. Add the Hazardous Materials spreadsheet
3. Add the ability to select a location on the map
4. After selecting a location, choose hazardous material
5. This places a buffer of area that needs to be evacuated

```{r}
#Emergency Response Guidebook Spreadsheet
hazmat <- "https://www.phmsa.dot.gov/sites/phmsa.dot.gov/files/docs/English_TIHWR_Table_ERG2016.xlsx"

#set the file path where it'll download to
file_path <- "data/EmergencyResponseGuide"

#download from the URL to the filepath specified
download.file(hazmat, file_path)

#set up geocode to get latlon for location of spill
geocode("#whatever people enter in box", output = "latlon", source = "dsk")

#select hazardous material that spilled
head(hazmat)

#put buffer around geocoded location from what hazmat spreadsheet states
```


# Results

Show tables, plots, etc. and describe them.
```{r}
#install.packages("leaflet")
library(leaflet)
map <- leaflet() %>%
  #Add default OpenStreetMap map tiles
  addTiles() %>%
  addMarkers(lng=-78.798, lat=42.900) %>%
  fitBounds(-79.1, 42.5, -78.5, 43.1)
#Print the map
map
```


# Conclusions

What have you learned?  Are there any broader implications?

# References

